Group assignment

### 2022-11-05 Draft.Rmd
Update Draft.Rmd

### • Year and month
### 22636 records from the dataset are for the year 2017 and 32311 - for 2018.
```{r echo=FALSE}
kable(count(df2, year)) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```

@@

```{r echo=FALSE}
kable(count(df2,acctype_f) %>% arrange(desc(n))) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```

@@

### • As we can see from the graph below, the price increased for 6 countires, Slovakia being the only case in which the price dropped.
### The biggest jump in price was in Italy. In this country, the price in 2018 increased by 24 euros compared to 2017.
```{r}
df3 <- aggregate(trueprice ~ country + year, 
                 data=df2, 
                 function(x) { 
                   c(mean_price = mean(x)) 
                 })
ggplot(data = df3, aes(x=year, y=trueprice, fill=country)) + 
  geom_bar(stat='identity') + facet_wrap(~country) +
  geom_text(aes(label = round(trueprice)), vjust = -0.2) +
  scale_x_discrete() + ylim(0, 195) + 
  labs(x='Year(2017,2018)', y='Price for one night (in EUR)', fill='Country')
```

@@

```{r echo=FALSE, message=FALSE}
ggplot(df2, aes(x = distance, y = trueprice))+
  stat_summary_bin(fun = 'mean', bins = 80, 
                   geom = 'point', color = 'red',
                   size = 2) + 
  labs(x='Distance from the city center', y='Price for one night(in EUR)')
```

```{r echo=FALSE, message=FALSE}
ggplot(df2, aes(x = distance, y = trueprice))+
  stat_summary_bin(fun = 'mean', bins = 50, 
                   geom = 'point', color = 'red',
                   size = 2) + 
  labs(x='Distance from the city center', y='Price for one night(in EUR)') +
  xlim(0,25)
```

>>>>

### • Year and month
### 22270 records from the dataset are for the year 2017 and 31570 - for 2018.
```{r echo=FALSE}
kable(count(df2, year)) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```

@@

```{r echo=FALSE}
kable(count(df2,acctype_f) %>% arrange(desc(n))) %>%
  kableExtra::kable_styling(latex_options = "hold_position")
```

@@

### • As we can see from the graph below, the price increased for 6 countires, Slovakia being the only case in which the price dropped.
### The biggest jump in price was in Italy. In this country, the price in 2018 increased by 24 euros compared to 2017.

```{r echo=FALSE}
df3 <- aggregate(trueprice ~ country + year, 
                 data=df2, 
                 function(x) { 
                   c(mean_price = mean(x)) 
                 })
ggplot(data = df3, aes(x=year, y=trueprice, fill=country)) + 
  geom_bar(stat='identity') + facet_wrap(~country) +
  geom_text(aes(label = round(trueprice)), vjust = -0.2) +
  scale_x_discrete() + ylim(0, 195) + 
  labs(x='Year(2017,2018)', y='Price for one night (in EUR)', fill='Country')
```

@@

```{r echo=FALSE, message=FALSE}
ggplot(df2, aes(x = distance, y = trueprice))+
  stat_summary_bin(fun = 'mean', bins = 80, 
                   geom = 'point', color = 'red',
                   size = 2) + 
  labs(x='Distance from the city center (in miles)', y='Price for one night (in EUR)') +
  scale_x_continuous(limits = c(0, 35),
                     breaks=seq(from=0, to=35, by=2.5))
```
